### 2023-05-05 tesis_Luis/Chapter4/chapter4.tex
updated

\begin{center}
  \begin{figure}[h]	
    \centering
    \includegraphics[scale=.35]{Chapter4/2022Scanprorgam.png}
    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
    \label{scan_prog}
  \end{figure}
\end{center}

@@

To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed. The mean and error per super separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the $y$ projection. The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$. To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted. Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I specifically for BCID 282, but the same plot is created for every BCID.\\

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.18]{Chapter4/ss1_histo_bx282.png}
    \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
    \label{ss1_hist_282}
  \end{figure}
\end{center}

\begin{table}[h!]
  \begin{center}
    \caption{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
    \label{ss_per_bx}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period I}} & \multicolumn{1}{c}{}  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7712 & 0.0054\\
      \hline
      822 & 0.7744 & 0.0055\\ 
      \hline
      2944 & 0.7695 & 0.0057\\ 
      \hline
      3123 & 0.7469 & 0.0049\\ 
      \hline
      3302 & 0.7708 & 0.0049\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7665 \pm 0.0023$} & \multicolumn{1}{c}{}\\
%      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
    \end{tabular}
    \hspace{0.5cm}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period II}} & \multicolumn{1}{c}{ }  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7192 & 0.0048\\
      \hline
      822 & 0.7257 & 0.0057\\ 
      \hline
      2944 & 0.7292 & 0.0058\\ 
      \hline
      3123 & 0.7028 & 0.0052\\ 
      \hline
      3302 & 0.7208 & 0.0053\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7195 \pm 0.0024$} & \multicolumn{1}{c}{}
    \end{tabular}   
  \end{center}
\end{table}

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=.40\textwidth]{Chapter4/xscan.png}
\includegraphics[width=.40\textwidth]{Chapter4/yscan.png}\\
\caption[vdM1 BCID 282]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
\label{vdM1_282_XYscan}
\end{figure}
\end{center}
For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully. The evaluation of the goodness of fit is shown in Fig. \ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.025]{Chapter4/DGConst_chi2.png}
    \caption[chi2/ndof for all scan pairs]{ chi2/ndof for all the scan pairs.  where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans. It is important to note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{chi2/ndof}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.49\textwidth]{Chapter4/DGConst_CapSigma.png}
    \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
    \caption[$\Sigma_{x,y}$ and peak values for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{capsigma_peak}
  \end{figure}
\end{center}

@@

\begin{eqnarray}
\sigma_{vis}^{Avg}=\Biggl(\displaystyle\sum_{i} w_{i}\sigma_{vis}^{i} \Biggr)\Biggl(\sqrt{ \displaystyle\sum_{i} w_{i}} \Biggr)^{-2}
\label{average}
\end{eqnarray}

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
    \caption[$\sigma_{vis}$ per Scan]{ $\sigma_{vis}$  per scan.} 
    \label{sigmavis_perscan}
  \end{figure}
\end{center}

>>>>

\begin{center}
  \begin{figure}[h]	
    \centering
    \includegraphics[scale=.35]{Chapter4/2022Scanprorgam.png}
    \caption[2022 vdM scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
    \label{scan_prog}
  \end{figure}
\end{center}

@@

To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed. The mean and error per super separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the $y$ projection. The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$. To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted. Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I, specifically for BCID 282, but the same plot is created for every BCID.\\

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.30]{Chapter4/ss1_histo_bx282.png}
    \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
    \label{ss1_hist_282}
  \end{figure}
\end{center}

\begin{table}[h!]
  \begin{center}
    \caption[Background values for the two super separation periods]{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
    \label{ss_per_bx}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period I}} & \multicolumn{1}{c}{}  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7712 & 0.0054\\
      \hline
      822 & 0.7744 & 0.0055\\ 
      \hline
      2944 & 0.7695 & 0.0057\\ 
      \hline
      3123 & 0.7469 & 0.0049\\ 
      \hline
      3302 & 0.7708 & 0.0049\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7665 \pm 0.0023$} & \multicolumn{1}{c}{}\\
%      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
    \end{tabular}
    \hspace{0.5cm}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period II}} & \multicolumn{1}{c}{ }  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7192 & 0.0048\\
      \hline
      822 & 0.7257 & 0.0057\\ 
      \hline
      2944 & 0.7292 & 0.0058\\ 
      \hline
      3123 & 0.7028 & 0.0052\\ 
      \hline
      3302 & 0.7208 & 0.0053\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7195 \pm 0.0024$} & \multicolumn{1}{c}{}
    \end{tabular}   
  \end{center}
\end{table}

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=.45\textwidth]{Chapter4/xscan.png}
\includegraphics[width=.45\textwidth]{Chapter4/yscan.png}\\
\caption[Fit for the vdM1 BCIDs 282 (x and y directions)]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
\label{vdM1_282_XYscan}
\end{figure}
\end{center}
For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully. The evaluation of the goodness of fit is shown in Fig. \ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.030]{Chapter4/DGConst_chi2.png}
    \caption[$\chi^{2}$/ndof per BCID for all scan pairs]{ chi2/ndof for all the scan pairs.  where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans. It is important to note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{chi2/ndof}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.49\textwidth]{Chapter4/DGConst_CapSigma.png}
    \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
    \caption[$\Sigma_{x,y}$ and peak values per BCID for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{capsigma_peak}
  \end{figure}
\end{center}

@@

\begin{eqnarray}
\sigma_{vis}^{Avg}=\Biggl(\displaystyle\sum_{i} w_{i}\sigma_{vis}^{i} \Biggr)\Biggl( \displaystyle\sum_{i} w_{i} \Biggr)^{-1}
\label{average}
\end{eqnarray}

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
    \caption[$\sigma_{vis}$ average per scan and final result]{ $\sigma_{vis}$  per scan.} 
    \label{sigmavis_perscan}
  \end{figure}
\end{center}

### 2023-05-05 tesis_Luis/chap_originales/Chapter4/chapter4.tex
updated

\begin{center}
  \begin{figure}[h]	
    \centering
    \includegraphics[scale=.35]{Chapter4/2022Scanprorgam.png}
    \caption[2022 vdM scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
    \label{scan_prog}
  \end{figure}
\end{center}

@@

To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed. The mean and error per super separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the $y$ projection. The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$. To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted. Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I, specifically for BCID 282, but the same plot is created for every BCID.\\

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.30]{Chapter4/ss1_histo_bx282.png}
    \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
    \label{ss1_hist_282}
  \end{figure}
\end{center}

\begin{table}[h!]
  \begin{center}
    \caption[Background values for the two super separation periods]{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
    \label{ss_per_bx}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period I}} & \multicolumn{1}{c}{}  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7712 & 0.0054\\
      \hline
      822 & 0.7744 & 0.0055\\ 
      \hline
      2944 & 0.7695 & 0.0057\\ 
      \hline
      3123 & 0.7469 & 0.0049\\ 
      \hline
      3302 & 0.7708 & 0.0049\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7665 \pm 0.0023$} & \multicolumn{1}{c}{}\\
%      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
    \end{tabular}
    \hspace{0.5cm}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period II}} & \multicolumn{1}{c}{ }  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7192 & 0.0048\\
      \hline
      822 & 0.7257 & 0.0057\\ 
      \hline
      2944 & 0.7292 & 0.0058\\ 
      \hline
      3123 & 0.7028 & 0.0052\\ 
      \hline
      3302 & 0.7208 & 0.0053\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7195 \pm 0.0024$} & \multicolumn{1}{c}{}
    \end{tabular}   
  \end{center}
\end{table}

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=.45\textwidth]{Chapter4/xscan.png}
\includegraphics[width=.45\textwidth]{Chapter4/yscan.png}\\
\caption[Fit for the vdM1 BCIDs 282 (x and y directions)]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
\label{vdM1_282_XYscan}
\end{figure}
\end{center}
For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully. The evaluation of the goodness of fit is shown in Fig. \ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.030]{Chapter4/DGConst_chi2.png}
    \caption[$\chi^{2}$/ndof per BCID for all scan pairs]{ chi2/ndof for all the scan pairs.  where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans. It is important to note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{chi2/ndof}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.49\textwidth]{Chapter4/DGConst_CapSigma.png}
    \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
    \caption[$\Sigma_{x,y}$ and peak values per BCID for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{capsigma_peak}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
    \caption[$\sigma_{vis}$ average per scan and final result]{ $\sigma_{vis}$  per scan.} 
    \label{sigmavis_perscan}
  \end{figure}
\end{center}

>>>>

\begin{center}
  \begin{figure}[h]	
    \centering
    \includegraphics[scale=.35]{Chapter4/2022Scanprorgam.png}
    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
    \label{scan_prog}
  \end{figure}
\end{center}

@@

To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed. The mean and error per super separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the $y$ projection. The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$. To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted. Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I specifically for BCID 282, but the same plot is created for every BCID.\\

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.18]{Chapter4/ss1_histo_bx282.png}
    \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
    \label{ss1_hist_282}
  \end{figure}
\end{center}

\begin{table}[h!]
  \begin{center}
    \caption{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
    \label{ss_per_bx}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period I}} & \multicolumn{1}{c}{}  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7712 & 0.0054\\
      \hline
      822 & 0.7744 & 0.0055\\ 
      \hline
      2944 & 0.7695 & 0.0057\\ 
      \hline
      3123 & 0.7469 & 0.0049\\ 
      \hline
      3302 & 0.7708 & 0.0049\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7665 \pm 0.0023$} & \multicolumn{1}{c}{}\\
%      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
    \end{tabular}
    \hspace{0.5cm}
    \begin{tabular}{|c | c | c | }
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period II}} & \multicolumn{1}{c}{ }  \\
      \hline
 \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
     \hline %\midrule[1.1pt]
      282 & 0.7192 & 0.0048\\
      \hline
      822 & 0.7257 & 0.0057\\ 
      \hline
      2944 & 0.7292 & 0.0058\\ 
      \hline
      3123 & 0.7028 & 0.0052\\ 
      \hline
      3302 & 0.7208 & 0.0053\\ 
      \hline
      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7195 \pm 0.0024$} & \multicolumn{1}{c}{}
    \end{tabular}   
  \end{center}
\end{table}

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=.40\textwidth]{Chapter4/xscan.png}
\includegraphics[width=.40\textwidth]{Chapter4/yscan.png}\\
\caption[vdM1 BCID 282]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
\label{vdM1_282_XYscan}
\end{figure}
\end{center}
For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully. The evaluation of the goodness of fit is shown in Fig. \ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.025]{Chapter4/DGConst_chi2.png}
    \caption[chi2/ndof for all scan pairs]{ chi2/ndof for all the scan pairs.  where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans. It is important to note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{chi2/ndof}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.49\textwidth]{Chapter4/DGConst_CapSigma.png}
    \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
    \caption[$\Sigma_{x,y}$ and peak values for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.} 
    \label{capsigma_peak}
  \end{figure}
\end{center}

@@

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
    \caption[$\sigma_{vis}$ per Scan]{ $\sigma_{vis}$  per scan.} 
    \label{sigmavis_perscan}
  \end{figure}
\end{center}
